\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-03 short.tex
first poster commit

\begin{icmlauthorlist}
\icmlauthor{Kevin Ellis}{MIT}
\icmlauthor{Lucas Morales}{MIT}
\icmlauthor{Matthias}{MIT}
\icmlauthor{Maxwell Nye}{MIT}
\icmlauthor{Armando Solar-Lezama}{MIT}
\icmlauthor{Joshua B. Tenenbaum}{MIT}
\end{icmlauthorlist}

@@

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

@@

  \end{tabular}
  \\\bottomrule\\
\end{tabular}}\vspace{-0.5cm}
\caption{Top: Tasks from three domains we apply our algorithm to, each followed by the programs \system discovers for them. Bottom: Several examples from learned DSL. Notice that learned DSL primitives can call each other, and that \system rediscovers higher-order functions like \code{filter} ($f_1$ under List Functions)}\label{initialExampleDSL}\vspace{-0.5cm}
\end{table*}
%% Because any learning problem can in principle be cast as
%% program induction, it is important to delimit our focus.  
In contrast
to computer assisted programming~\cite{solar2008program} or genetic
programming~\cite{DBLP:books/daglib/0070933}, our goal is not to automate software
engineering, or to synthesize large bodies of code starting from scratch.  Ours is a basic AI goal:
capturing the human ability to learn to think flexibly and efficiently
in new domains --- to learn what you need to know about a domain so you
don't have to solve new problems starting from scratch.  %% We are
%% focused on problems that people solve relatively
%% quickly, once they acquire the relevant domain expertise.  These
%% correspond to tasks solved by short programs --- if you have an
%% expressive DSL.
%% Even with a good DSL, program search may be
%% intractable;
%
% , and adding new library routines to the DSL only broadens the
% search space;
%
%% so we train a
%% neural network to guide the search procedure.

>>>>

\begin{icmlauthorlist}
\icmlauthor{Kevin Ellis}{MIT}
\icmlauthor{Lucas Morales}{MIT}
\icmlauthor{Mathias Sabl\'e Meyer}{MIT}%\icmlauthor{Matthias}{MIT}
\icmlauthor{Armando Solar-Lezama}{MIT}
\icmlauthor{Joshua B. Tenenbaum}{MIT}
\end{icmlauthorlist}

@@

\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
%\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

@@

  \end{tabular}
  \\\bottomrule\\
\end{tabular}}\vspace{-0.5cm}
\caption{Top: Tasks from three domains we apply our algorithm to, each followed by the programs \system discovers for them. Bottom: Several examples from learned DSL. Notice that learned DSL primitives can call each other, and that \system rediscovers higher-order functions like \code{filter} ($f_1$ under List Functions)}\label{initialExampleDSL}%\vspace{-0.5cm}
\end{table*}
%% Because any learning problem can in principle be cast as
%% program induction, it is important to delimit our focus.  
In contrast
to computer assisted programming~\cite{solar2008program} or genetic
programming~\cite{DBLP:books/daglib/0070933}, our goal is not to automate software
engineering, or to synthesize large bodies of code starting from scratch.  Ours is a basic AI goal:
capturing the human ability to learn to think flexibly and efficiently
in new domains --- to learn what you need to know about a domain so you
don't have to solve new problems starting from scratch.  %% We are
%% focused on problems that people solve relatively
%% quickly, once they acquire the relevant domain expertise.  These
%% correspond to tasks solved by short programs --- if you have an
%% expressive DSL.
%% Even with a good DSL, program search may be
%% intractable;
%
% , and adding new library routines to the DSL only broadens the
% search space;
%
%% so we train a
%% neural network to guide the search procedure.
